Naturalness and Long-Lived Beyond the Standard Model Particles

### 2017-08-07 tex/draft.tex
Actual last edits before submitting

    When calculating contributions from loop diagrams, one finds that fermion loops differ in sign from boson loops, which means that in SUSY every bosonic correction to the Higgs mass is cancelled by a fermionic correction and vice versa. In fact, exact supersymmetry predicts that the bare Higgs mass is uncorrected to all orders in perturbation theory, as shown in Fig.~\ref{exact_susy_correction} below~\cite{primer}.

@@

        The authors minimize the effect of hadronic interactions by vetoing the material-dense regions of the detector (see Fig.~\ref{material_map}) and estimate the residual background by extrapolating from the low-mass region, which is dominated by hadronic interactions. After a dedicated study, the background from merged vertices was found to be negligible. Finally, the background from crossing tracks is determined from a model that adds fake tracksto data vertices.

@@

        \noindent \begin{figure}[htbp] \begin{center}
        \begin{subfigure}[htbp]{0.32\textwidth} \begin{center}
        \includegraphics[width=\textwidth]{images/disappearing_ew_limit}
        \end{center} \end{subfigure}
        \begin{subfigure}[htbp]{0.32\textwidth} \begin{center}
        \includegraphics[width=\textwidth]{images/disappearing_qcd_200ps_limit}
        \end{center} \end{subfigure}
        \begin{subfigure}[htbp]{0.32\textwidth} \begin{center}
        \includegraphics[width=\textwidth]{images/disappearing_qcd_1ns_limit}
        \end{center} \end{subfigure}
        \caption{Limits on chargino mass and lifetime in the electroweak production channel (left) and gluino and chargino masses in the gluon pair-production channel with a \SI{0.2}{\nano\s} (center) and \SI{1.0}{\nano\s} chargino lifetime~\cite{atlas_disappearing}.}
        \label{disappearing_limits}
        \end{center} \end{figure}

@@

    Combining results from several searches can also elucidate new directions for important searches. By recasting several LLP searches similar to those described in Sec.~\ref{analyses}, Evans and Shelten looked at the current viability of several SUSY spectra that predict long-lived staus. They identified significant gaps in coverage for models with displaced taus or same-sign displaced leptons, signals that appear in several well-motivated models such as GMSB, where staus are commonly the NLSP, and RPV, where certain couplings lead to same-flavor leptons~\cite{ll_staus}.

>>>>

    When calculating contributions from loop diagrams, one finds that fermion loops differ in sign from boson loops, which means that in SUSY every bosonic correction to the Higgs mass is cancelled by a fermionic correction and vice versa. In fact, exact supersymmetry predicts that the bare Higgs mass is uncorrected to all orders in perturbation theory~\cite{primer}. Fig.~\ref{exact_susy_correction} shows the leading-order cancellation.

@@

        The authors minimize the effect of hadronic interactions by vetoing the material-dense regions of the detector (see Fig.~\ref{material_map}) and estimate the residual background by extrapolating from the low-mass region, which is dominated by hadronic interactions. After a dedicated study, the background from merged vertices was found to be negligible. Finally, the background from crossing tracks is determined from a model that adds fake tracks to data vertices.

@@

        \noindent \begin{figure}[htbp] \begin{center}
        \begin{subfigure}[htbp]{0.32\textwidth} \begin{center}
        \includegraphics[width=\textwidth]{images/disappearing_ew_limit}
        \end{center} \end{subfigure}
        \begin{subfigure}[htbp]{0.32\textwidth} \begin{center}
        \includegraphics[width=\textwidth]{images/disappearing_qcd_200ps_limit}
        \end{center} \end{subfigure}
        \begin{subfigure}[htbp]{0.32\textwidth} \begin{center}
        \includegraphics[width=\textwidth]{images/disappearing_qcd_1ns_limit}
        \end{center} \end{subfigure}
            \caption{Limits on chargino mass and lifetime in the electroweak production channel (left) and gluino and chargino masses in the gluon pair-production channel with a \SI{0.2}{\nano\s} (center) and \SI{1.0}{\nano\s} (right) chargino lifetime~\cite{atlas_disappearing}.}
        \label{disappearing_limits}
        \end{center} \end{figure}

@@

    Combining results from several analyses can also elucidate new directions for important searches. By recasting several LLP searches similar to those described in Sec.~\ref{analyses}, Evans and Shelten looked at the current viability of several SUSY spectra that predict long-lived staus. They identified significant gaps in coverage for models with displaced taus or same-sign displaced leptons, signals that appear in several well-motivated models such as GMSB, where staus are commonly the NLSP, and RPV, where certain couplings lead to same-flavor leptons~\cite{ll_staus}.
